Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex
progressing on exp

Quantitative results are given in Tab.~\ref{tab:pascal12} in terms of
AP and AVP and in Fig.~\ref{fig:car_cnn_ap} in terms of
precision-recall plots and viewpoint confusion matrices. Example
outputs of our method applied to candidate object detections are given
in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
visualized in Fig.~\ref{}.

@@

The second observation is that the fine-tuning based on MCMC can
indeed improve pose estimation performance slightly, e.g., by $1.1$
for bicycle-16v and using the DPM-VOC+VP as the base detector, or by
$1.1$ for bicycle-16v when using the R-CNN as the base detector.

% We got significant improvement on viewpoint estimation by using our
% method on top of general purpose detectors. Note that our method
% estimates azimuth, elevation, in-plane rotation, focal length
% estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
% estimate discrete viewpoints.

@@

\subsection{Stability of Our Method for Irregular Bounding Boxes}

% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections,

R-CNN detection bounding boxes are irregular in shape since they come from other region proposal methods and sometimes they truncate objects. To handle such irregular shape and truncation, we added small context around the bounding boxes and run our method.

>>>>

Quantitative results are given in Tab.~\ref{tab:pascal12} in terms of
AP and AVP and in Fig.~\ref{fig:car_cnn_ap} in terms of
precision-recall plots and viewpoint confusion matrices. Example
outputs of our method applied to candidate object detections are given
in Fig.~\ref{fig:pascal12cnn}, and the effect of fine-tuning is
visualized in Fig.~\ref{fig:tuning}.

@@

The second observation is that the fine-tuning based on MCMC can
indeed improve pose estimation performance slightly, e.g., by $1.1$
for bicycle-16v and using the DPM-VOC+VP as the base detector, or by
$1.1$ for bicycle-16v when using the R-CNN as the base detector.
%
In Fig.~\ref{fig:tuning}, we visualize the effect of fine-tuning
qualitatively for two different test images. In both cases, the
fine-tuned visually comes closer to the true 3D pose.
% We got significant improvement on viewpoint estimation by using our
% method on top of general purpose detectors. Note that our method
% estimates azimuth, elevation, in-plane rotation, focal length
% estimation, fine-grained categorization whereas V-DPM, VOC-DPM only
% estimate discrete viewpoints.

@@

\paragraph{Robustness.}
% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections, 
While the R-CNN detector~\cite{Girshick14} is highly robust to
variations in object appearance and even occlusion and truncation,
the resulting bounding box detections vary largely in the object
portions that they contain  -- notably, they might

In Fig.~\ref{}, we visualize the effect

accomodate

 are irregular in
shape since they come from other region proposal methods and sometimes
they truncate objects. To handle such irregular shape and truncation,
we added small context around the bounding boxes and run our method.
